analyze_growth

### 2023-12-19 smelt_2019_allseasons/analyze_growth.Rmd

```{r}
hist(Summer$FL_cm_Pre)
hist(filter(Summer, Site=="RV")$FL_cm_Post)
hist(Summer$Weight_g_Pre)
hist(filter(Summer, Site=="RV")$Weight_g_Post)

@@

hist(Fall$FL_cm)
hist(Fall$Weight_g)
hist(Fall$K)

@@

  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
     geom_text( aes(label = .group, x = Season, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Proportional Change in K (g cm^-2) with 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        axis.text.y = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

(plot_season_wt <- ggplot(data = letter_m2,) + 
   geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +

  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
   geom_text( aes(label = .group, x = Season, y = upper.CL + 0.02), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
    viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Proportional Change in Weight (g) with 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

  geom_segment(aes(x = Site, y = emmean, xend = Site, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
    geom_segment(aes(x = Site, y = emmean, xend = Site, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
      geom_errorbar(aes(x = Site, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
    geom_text( aes(label = .group, x = Site, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
  geom_point( aes(x=Site, y=emmean), size = 2.5, shape = 18) +     
  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Change in K (g cm^-2) with 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        axis.text.y = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

  geom_segment(aes(x = Site, y = emmean, xend = Site, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
    geom_segment(aes(x = Site, y = emmean, xend = Site, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
   geom_errorbar(aes(x = Site, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
    geom_point( aes(x=Site, y=emmean), size = 2.5, shape = 18) +     
   geom_text( aes(label = .group, x = Site, y = upper.CL + 0.03), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
    viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Change in Weight (g) with 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

>>>>

```{r}
ggplot(filter(Summer, Site == "FCCL")) + 
  geom_histogram(aes(FL_cm, color = Period, alpha = 0.5, fill = Period), binwidth = 0.2) +
  facet_wrap(~Period, nrow = 2)
ggplot(filter(Summer, Site == "FCCL")) + 
  geom_histogram(aes(Weight_g, fill = Period, alpha = 0.5, color = Period)) +
  facet_wrap(~Period, nrow = 2)
ggplot(filter(Summer, Site == "FCCL")) + 
  geom_histogram(aes(K, fill = Period, alpha = 0.5, color = Period)) +
  facet_wrap(~Period, nrow = 2)

ggplot(filter(Summer, Site == "RV")) + 
  geom_histogram(aes(FL_cm))
ggplot(filter(Summer, Site == "RV")) + 
  geom_histogram(aes(Weight_g))

@@

ggplot(filter(Fall, Site == "FCCL")) + 
  geom_histogram(aes(FL_cm, color = Period, alpha = 0.5, fill = Period), binwidth = 0.2) +
  facet_wrap(~Period, nrow = 2)
ggplot(filter(Fall, Site == "FCCL")) + 
  geom_histogram(aes(Weight_g, fill = Period, alpha = 0.5, color = Period)) +
  facet_wrap(~Period, nrow = 2)

@@

  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
     geom_text( aes(label = .group, x = Season, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
     annotate(geom = "text", x = 3.2, y = 0.1, label = "B", size = 8) +
  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Proportional Change in K \nwith 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        axis.text.y = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

(plot_season_wt <- ggplot(data = letter_m2) + 
   geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +

  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
   geom_text( aes(label = .group, x = Season, y = upper.CL + 0.02), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
     annotate(geom = "text", x = 3.2, y = 0.24, label = "A", size = 8) +
    viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Proportional Change in Weight \nwith 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

  geom_segment(aes(x = Site, y = emmean, xend = Site, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
    geom_segment(aes(x = Site, y = emmean, xend = Site, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
      geom_errorbar(aes(x = Site, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
    geom_text( aes(label = .group, x = Site, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
        annotate(geom = "text", x = 4.1, y = -0.005, label = "D", size =8) +
  geom_point( aes(x=Site, y=emmean), size = 2.5, shape = 18) +     
  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Proportional Change in K \nwith 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        axis.text.y = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

  geom_segment(aes(x = Site, y = emmean, xend = Site, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
    geom_segment(aes(x = Site, y = emmean, xend = Site, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
   geom_errorbar(aes(x = Site, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
    geom_point( aes(x=Site, y=emmean), size = 2.5, shape = 18) +     
   geom_text( aes(label = .group, x = Site, y = upper.CL + 0.03), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
    annotate(geom = "text", x = 4.1, y = -0.02, label = "C", size = 8) +
    viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Proportional Change in Weight \nwith 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

##### Both season and site
```{r}
library(patchwork)
png(filename = "smelt_2019_allseasons/figures/model_season_site.png", height = 8, width = 8,units = "in", 
    res = 300, pointsize = 12, family = "sans")
(plot_season_wt & plot_season_k) / (plot_Site_wt & plot_Site_k)
dev.off()
```
